%----------- PUBLICATIONS -----------

% @TODO
% Counter for paper index
% Automatically make bold Author name
% Set commas of the page numbers in the command definition

\section{Publications}


    \itemizeCVBegin[nolabel]{Journals}

        \publicationsItem
            {[5] F. Heiding, \textbf{E. Suren}, J. Olegård, R. Lagerström.}
            {Penetration testing of connected households.}
            {Computers \& Security}
            {, 126:103067, }
            {February 2023}

        \publicationsItem
            {[4] \textbf{E. Suren}, F. Heiding, J. Olegård, R. Lagerström.} 
            {PatrIoT: Practical and agile threat research for IoT.} 
            {International Journal of Information Security (IJIS'22)}
            {, 213–233, }
            {December 2022}

        \publicationsItem
            {[3] \textbf{E. Suren}.} 
            {ZEKI: Unsupervised Zero-day Exploit Kit Intelligence.} 
            {Turkish Journal of Electrical Engineering \& Computer Sciences (TJEECS'20)}
            {, 28(5):1859-1870, } 
            {March 2020}

        \publicationsItem
            {[2] \textbf{E. Suren}, P. Angin, N. Baykal.} 
            {I see EK: A Lightweight Technique to Reveal Exploit Kit family by Overall URL Patterns of Infection Chains.} 
            {Turkish Journal of Electrical Engineering \& Computer Sciences (TJEECS'19)}
            {, 27(5):3713-3728, }
            {September 2019}

        \publicationsItem
            {[1] \textbf{E. Suren} and P. Angin.}
            {Know Your EK: A Content and Workflow Analysis Approach for Exploit Kits.}
            {Journal of Internet Services and Information Security (JISIS'19)}
            { , 9(1):24–47, }
            {February 2019}

    \itemizeCVEnd


    \itemizeCVBegin[nolabel]{Conference Proceedings}

        \publicationsItem
            {[1] Ciklabakkal, Ege and Donmez, Ataberk and Erdemir, Mert and \textbf{Suren, Emre} and Yilmaz, Mert Kaan and Angin, Pelin.} 
            {ARTEMIS: An intrusion detection system for MQTT attacks in Internet of Things.}
            {38th Symposium on Reliable Distributed Systems (SRDS'19)}
            {, 369-3692, }
            {October 2019}
        
    \itemizeCVEnd